Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-05-02 accessPEP.Rmd
plotting ttimes

## Files
source("R/utils.R")
source("R/models.R")
source("R/data_functions.R")
source("R/get.burden.R")
select <- dplyr::select
knitr::opts_chunk$set(fig.pos = 'h', echo = FALSE, message = FALSE, warning = FALSE, 
                      include = TRUE, cache.lazy = FALSE)
```

>>>>

## Files
source("R/utils.R")
source("R/models.R")
source("R/data_functions.R")
source("R/get.burden.R")
select <- dplyr::select
knitr::opts_chunk$set(fig.pos = 'h', echo = FALSE, message = FALSE, warning = FALSE, 
                      include = TRUE, cache.lazy = FALSE)

## Travel times
ttimes <- raster("output/ttimes_masked.tif")
gg_SD <- fortify(SD_shape, region = "VILLCODE")

##### Getting raster of coverage
library(rasterVis)
library(patchwork)
library(animation)
ctar_metadata <- read.csv("data/ctar_metadata.csv")
gplot(ttimes) +
  geom_raster(aes(fill = value/60)) +
  scale_fill_gradient(low = "white", high = "red", na.value = "white", 
                      name = "Travel times \n (hours)") +
  geom_point(data = ctar_metadata, aes(x = LONGITUDE, y = LATITUDE), 
             color = "blue", alpha = 0.5) +
  theme_void() +
  coord_equal()

## Travel times
ttimes_best <- raster("output/ttimes_best.tif")
gps_locs <- read.csv(file = "data/ctar_metadata.csv", stringsAsFactors = FALSE)[,c(1, 3, 4)]
names(gps_locs) <- c ("CTAR", "X_COORD", "Y_COORD")

## candidate points
csbs <- read.csv("data/csbs.csv", stringsAsFactors = FALSE)
csbs %>% 
  dplyr::filter(type == "CSB2", genre_fs != "Priv", type_fs != "Health Post") %>%
  dplyr::select(CTAR = nom_fs, X_COORD = ycoor, Y_COORD = xcoor) -> csbs

point_mat <- rbind(gps_locs, csbs)
##### Getting raster of coverage
library(rasterVis)
library(patchwork)
library(animation)
gplot(ttimes_best) +
  geom_raster(aes(fill = value/60)) +
  scale_fill_gradient(low = "white", high = "red", na.value = "white", 
                      name = "Travel times \n (hours)") +
  geom_point(data = point_mat, aes(x = Y_COORD, y = X_COORD), color = "blue", alpha = 0.25) +
  theme_void() +
  coord_equal()

pop10 <- raster("output/pop10.tif")
prop_pop <- pop10/sum(values(pop10), na.rm = TRUE)

## baseline proportion
threshold = 3 # threshold # of hours to calculate the proportion of pop at
sum(prop_pop[ttimes >= 60*threshold], na.rm = TRUE)
sum(prop_pop[ttimes_best >= 60*5], na.rm = TRUE)
